Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-10 exp1/iswc2013.tex
add some more p-values
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@564 43ef1190-90fd-4dd7-a769-d0121f02b80e

The resulting normal plot is in figure~\ref{fig:frac32normal}. We see
that only two main effects are significant on a $\alpha = 0.05$ level
according to the Lenth criterion, ``Implement'' is again deemed a
significant improvement, and ``Union'' is deemed significantly the
hardest operation for the query engine. We see that some other points
also deviate from the straight line, but with as few runs as this, the
total variance is great, so no other conclusions can be drawn. We may
use the t-test we used in the previous section, as we have only two
active factors and so we may treat it as a $2^2$ experiment with 8
repetitions, but we must expect a higher p-value due to the larger
variance.

@@

Since the 64-run experiment also has 3 inactive factors, ``Machine'',
``TripleC'' and ``Range'', we can again treat it as a $2^5$ experiment
replicated twice. Using the same procedure as above, we find that
again, the hypothesis test indicates that the new implementation is an
improvement at $p = 5.9 \cdot 10^{-6}$. The comparatively higher p-value
is due to the lower number of runs. It is also possible to perform the
per-environmental test, but we refrain from that in the interest of
brevity.\todo{good way to say it?}

>>>>

The resulting normal plot is in figure~\ref{fig:frac32normal}. We see
that only two main effects are significant on a $\alpha = 0.05$ level
according to the Lenth criterion, ``Implement'' is again deemed a
significant improvement, and ``Union'' is deemed significantly the
hardest operation for the query engine. We see that some other points
also deviate from the straight line, but with as few runs as this, the
total variance is great, so no other conclusions can be drawn. We may
use the t-test we used in the previous section, as we have only two
active factors and so we may treat it as a $2^2$ experiment with 8
replications, but the resulting $p = 0.00098$ must be expected with
such a small number of runs and thus higher variance.

@@

Since the 64-run experiment has 3 inactive factors, ``Machine'',
``TripleC'' and ``Range'', we can again treat it as a $2^5$ experiment
replicated twice. Using the same procedure as above, we find that
again, the hypothesis test indicates that the new implementation is an
improvement at $p = 5.9 \cdot 10^{-6}$. Again, the comparatively higher p-value
is due to the lower number of runs. It is also possible to perform the
per-environmental test.
